### 2021-02-24 paper/fse21/related.tex
Fixed typos.

\section{Related Work}\label{sec:related}
Researchers have introduced various technique to utilize dynamic
analysis for static analysis in three ways: combined analysis,
automatic modeling, and pruning analysis scope.

\paragraph{Combined Analysis}
The most related previous work is combined analysis that utilizes dynamic
analysis during Java static analysis introduced by \citet{concerto}.
They proved that their combined analysis is sound and showed that it could
significantly improve the precision and performance of Java static analysis by
evaluating their tool, \concerto.  However, their approach has several
limitations compared with dynamic shortcuts.  First, it syntactically
divides a given program to \textit{applications} parts for static
analysis and \textit{frameworks} parts for dynamic analysis.  Thus, it is impossible to
freely switch between static analysis and dynamic analysis.  It is
even impossible to perform both static and dynamic analysis of 
the same program part in different contexts.  In addition, while they
introduced \textit{mostly-concrete interpretation} similar to our
sealed symbolic execution, it supports only a special \textit{unknown}
value that represents any possible value.  Thus, it cannot preserve
the precision of complex abstract domains~\cite{revisit-recency,
  regex, weaklySPE} frequently used in JavaScript static analysis.
On the contrary, sealed symbolic execution automatically detects when
to switch to static analysis to use abstract semantics for abstract values.
Finally, \concerto preserves the soundness when a program satisfies
the \textit{state separation hypothesis}.  It assumes that the states
of application parts and framework parts are not interrogated
or manipulated by each other.  While the assumption may be reasonable
for static analysis of Java applications using external libraries, it
is not satisfied for JavaScript programs in general.  Unlike their
approach, our approach does not have any assumptions between static and
dynamic analysis parts.

@@

\paragraph{Pruning Analysis Scope}
Another approach to utilize dynamic analysis for JavaScript static analysis is
to prune the scope of analysis.  \citet{determinacy} proposed dynamic
determinacy analysis, which infers determinacy facts like whether a
variable or an expression at a given location holds the same value in
all possible execution of a program via concrete execution.
They specialized target source code with determinacy
facts so that static analysis can get benefits from elimination of dynamic code
generation such as \jscode{eval} and constant property names.
\citet{blended} introduced \textit{blended taint analysis}, which specializes JavaScript dynamic
language features such as dynamic code generation or variadic function calls.
It first performs dynamic analysis to collect traces with concrete values used
in dynamic language features and restricts the semantics of features based on the
collected traces during static analysis.  \citet{battles, eha} utilize three different points to reduce
analysis scope: initial states, dynamically loaded files, and event handlers.
They dumped the initial states from a specific web browser to focus on
analysis of the behaviors of web applications running on the browser.
Then, they collected paths of dynamically loaded files via concrete
execution and utilized the path information in static analysis.
For event handlers, they intentionally analyzed partial execution flows using concrete user events.
They collected concrete states for each entry of an event handler
during dynamic analysis, merged them to a single abstract state, and analyzed
the event handler with the abstract state.
Unfortunately, all the above mentioned approaches do not preserve
soundness of static analysis unlike our approach using dynamic shortcuts.

>>>>

\section{Related Work}\label{sec:related}
Researchers have introduced various techniques to utilize dynamic
analysis for static analysis in three ways: combined analysis,
automatic modeling, and pruning analysis scope.

\paragraph{Combined Analysis}
The most related previous work is combined analysis that utilizes dynamic
analysis during Java static analysis introduced by \citet{concerto}.
They proved that their combined analysis is sound and showed that it could
significantly improve the precision and performance of Java static analysis by
evaluating their tool, \concerto.  However, their approach has several
limitations compared with dynamic shortcuts.  First, it syntactically
divides a given program to \textit{applications} parts for static
analysis and \textit{frameworks} parts for dynamic analysis.  Thus, it is impossible to
freely switch between static analysis and dynamic analysis.  It is
even impossible to perform both static and dynamic analysis of 
the same program part in different contexts.  In addition, while they
introduced \textit{mostly-concrete interpretation} similar to our
sealed symbolic execution, it supports only a special \textit{unknown}
value that represents any possible value.  Thus, it cannot preserve
the precision of complex abstract domains~\cite{revisit-recency,
  regex, weaklySPE} frequently used in JavaScript static analysis.
On the contrary, sealed symbolic execution automatically detects when
to switch to static analysis to use abstract semantics for abstract values.
Finally, \concerto\ preserves the soundness when a program satisfies
the \textit{state separation hypothesis}.  It assumes that the states
of application parts and framework parts are not interrogated
or manipulated by each other.  While the assumption may be reasonable
for static analysis of Java applications using external libraries, it
is not satisfied for JavaScript programs in general.  Unlike their
approach, our approach does not have any assumptions between static and
dynamic analysis parts.

@@

\paragraph{Pruning Analysis Scope}
Another approach to utilize dynamic analysis for JavaScript static analysis is
to prune the scope of analysis.  \citet{determinacy} proposed dynamic
determinacy analysis, which infers determinacy facts like whether a
variable or an expression at a given location holds the same value in
all possible execution of a program via concrete execution.
They specialized target source code with determinacy
facts so that static analysis can get benefits from elimination of dynamic code
generation such as \jscode{eval} and constant property names.
\citet{blended} introduced \textit{blended taint analysis}, which specializes JavaScript dynamic
language features such as dynamic code generation or variadic function calls.
It first performs dynamic analysis to collect traces with concrete values used
in dynamic language features and restricts the semantics of features based on the
collected traces during static analysis.  \citet{battles, eha} utilize three different points to reduce
analysis scope: initial states, dynamically loaded files, and event handlers.
They dumped the initial states from a specific web browser to focus on
analysis of the behaviors of web applications running on the browser.
Then, they collected paths of dynamically loaded files via concrete
execution and utilized the path information in static analysis.
For event handlers, they intentionally analyzed partial execution flows using concrete user events.
They collected concrete states for each entry of an event handler
during dynamic analysis, merged them to a single abstract state, and analyzed
the event handler with the abstract state.
Unfortunately, all the above mentioned approaches except~\cite{determinacy} do not preserve
soundness of static analysis unlike our approach using dynamic shortcuts.
